---
---

Use the `hsls_small.dta` data set (the version used in this class) make plots that help answer each of the following questions

- Throughout, you **should** account for missing values by dropping them
- Do not worry about axis labels or other visual elements, that is covered next week

> Hint: You're going to need the [code book](https://nces.ed.gov/datalab/onlinecodebook) to identify the necessary variables

Also note, your final project proposals are due this week as well

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** How does student socioeconomic status differ between students who ever attended college and those who did not?

```{r}
#| label: 1a


```

## Question Two

**a)** How do educational expectations (of both students and parents) differ by high school completion status?

> Hint: You will want to borrow some code from last week's assignment here

```{r}
#| label: 2a


```

## Question Three

**a)** What is the relationship between student socioeconomic status and math test score?

```{r}
#| label: 3a


```


```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) and the rendered PDF to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
