---
---

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** Using a `for()` loop, read in the school test files from `data/sch-test/by-school/`.

```{r}
#| label: 1a


```


**b)** Do the same, but, only for Bend Gate and Niagara

```{r}
#| label: 1b


```

> Hint: Looking inside the `list.files()` help file for somewhere you might use some regex

**c)** Do it one more time, but include some code that add a column called `file_path` which contains the location where each row's information is coming from

```{r}
#| label: 1c


```

**d)** Bind the data sets from part **c)** together

```{r}
#| label: 1d


```

## Question Two

**a)** Read in `hsls-small.dta`

```{r}
#| label: 2a


```

**b)** Write a function that

1. Takes a `stu_id` as the input
2. `paste()`s back a sentence which says `if()` they ever attended college `else()` whether their parent expected them to go to college
  - If a student went to college it should return something like "this student went to college"
  - If they didn't, it should return something like "this student did not go to college, their students did/did not expect them to"
3. Optional: `if()` the student went to college, add a second sentence that says how many months they had between high school and going to college
4. Super-Optional: Following from that, edit the second sentence to include how that student's delay compares to the average delay (you can pick, mean or median)

```{r}
#| label: 2b


```


```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
