---
---

Use the `hsls_small.csv` data set from the lesson answer the following questions

- Throughout, you **should** account for missing values by dropping them

> Hint: You're going to need the [code book](https://nces.ed.gov/datalab/onlinecodebook) to identify the necessary variables

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** Compute the average test score by region

```{r}
#| label: 1a


```

**b)** Join back into the full data frame

```{r}
#| label: 1b


```

**c)** Compute the difference between each student's test score and that of the region

```{r}
#| label: 1c


```

**d)** Finally, show the mean of these differences by region

> Hint: If you think about it, this should probably be a very very small number...

```{r}
#| label: 1d


```

**e)** Optional: Do all of the above steps in one piped chain of commands

```{r}
#| label: 1e


```


## Question Two

**a)** Compute the average test score by region and family income level

```{r}
#| label: 2a


```

**b)** Join that average score back to the full data frame

> Hint: You can join on more than one key using `c()`

```{r}
#| label: 2b


```

**c)** Optional: Do all of the above steps in one piped chain of commands

```{r}
#| label: 2c


```

## Question Three

**a)** Select the following variables from the full data set

- `stu_id`
- `x1stuedexpct`
- `x1paredexpct`
- `x4evratndclg`  

```{r}
#| label: 3a


```

**b)** From this reduced data frame, reshape the data frame so that it is long in educational expectations

- As in, each observation should have two rows, one for each educational expectation type

*e.g. (your column names and values may be different)*

| stu_id | expect_type  | expectation | x4evratndclg |
|:------:|:------------:|:-----------:|:------------:|
|  0001  | x1stuedexpct |      6      |      1       |
|  0001  | x1paredexpct |      7      |      1       |
|  0002  | x1stuedexpct |      5      |      1       |
|  0002  | x1paredexpct |      5      |      1       |

```{r}
#| label: 3b


```

```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
