---
---

Good news! By the time you have completed the quick exercises in this class, you should have some of this assignment done!

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One (to be done in class)

**a)** Write a few sentences describing your proposal for your reproducible report

**b)** Add an appropriate section header (e.g. "Overview")

**c)** Add **bold face** around your dependent variable

**d)** Make your data source name *italic*

**e)** Add an appropriate title and author name to the YAML header 

## Question Two (to be done after class)

**a)** Read in at least one data file you intend to use for your final project

```{r}
#| label: 2a


```

**b)** Write a few sentences describing where you got the data from

**c)**  Add an appropriate header (e.g., "Data")

**d)** Summarize one or more continuous variable including

-   mean
-   standard deviation
-   minimum
-   maximum

**e)** Summarize one or more categorical variables including

-   count for each category
-   percentage of count for each category

> Hint: Remember how to get percentages from assignment 2

**f)** Save the file as `reproducible-report.qmd`

Congratulations, you've officially started the Quarto document for your final project!

```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
