---
---

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** Create an Excel spreadsheet called `r-class-family.xlsx` with three columns; `name`, `degree_program`, and `years_at_uf`

**b)** Add your information to it

**c)** Optional: Add some of your classmates information (recall from class introductions, or, re-introduce yourself after class)

**d)** Read this file into R and assign it to an object called `data` (just like we did in class)

> Hint: You'll need to load a new package to read Excel files, between Google and asking your friends, you should be able to figure it out

```{r}
#| label: 1d

```

## Question Two

**a)** Pick any single data file from IPEDS that peaks your interest from [IPEDS complete data files](https://nces.ed.gov/ipeds/datacenter/DataFiles.aspx)

**b)** Download it and save it to your `data` subfolder in your class folder

**c)** Read it into R and assign it to an object called `data_ipeds`

```{r}
#| label: 2c

```

```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.

FYI: This is a special kind of code block (a raw html comment) which is a great way of adding notes to your file that won't show up in the final pdf such as notes to yourself, feedback from reviewers, questions/prompts, etc.. It's also how I will give your assignment feedback. You don't need to worry about using them for now, but you might find them useful later on for planning your final projects etc.
-->
```
