---
---

For this week's assignment, you have two options, make another map similar to the one we made in class, or, make a map you can use in your final project

## Option One

Using the `tidycensus` package and code from this lesson, make a different point map following the instructions below:

1.  Modify the `tidycensus` code to download data for a different geography **and** a different variable
2.  Make a new base map
3.  Use the same academic libraries IPEDS data (or another IPEDS file if you want) to plot points on your new base map that change `aes()` based on a new variable

```{r}
#| label: option1


```

## Option Two

Using data from your final project (plus `tidycensus` and/or `tigris` as needed) make a map following the guidance from the lesson. This will take a bit more time now, but, if it makes sense for your final project it might save you time later.
    
- Note: It still needs to be a `geom_sf()`

> Hint: The main challenge will be working out how to either convert you data to spatial data or merge it with existing spatial data

```{r}
#| label: option2


```


```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
