---
---

Use the `hsls_small.csv` data set from the lesson answer the following questions

- Throughout, you **should** account for missing values by dropping them

> Hint: You're going to need the [code book](https://nces.ed.gov/datalab/onlinecodebook) to identify the necessary variables

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One

**a)** What is the average (mean) standardized math score?

```{r}
#| label: 1a


```

**b)** How does this differ by gender?

```{r}
#| label: 1b


```

## Question Two

**a)** Among those students who are under 185% of the federal poverty line in the base year of the survey, what is the median household income category? (Include a description what that category represents)

```{r}
#| label: 2a


```

## Question Three

**a)** Of the students who earned a high school credential (traditional diploma or GED), what percentage earned a GED or equivalency?

```{r}
#| label: 3a


```

**b)** How does this differ by region?

```{r}
#| label: 3b


```

## Question Four

**a)** What percentage of students ever attended a post-secondary institution? (as of the data collection in february 2016)

```{r}
#| label: 4a


```

**b)** Give the cross tabulation for both family incomes above/below \$35,000 and region\

- This means you should have percentages for 8 groups: above/below \$35,000 within each region 

> Hint: `group_by()` can be given more than one group

```{r}
#| label: 4b


```

```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) and the PDF rendered to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```
