---
---

Good news! By the time you have completed the quick exercises in this class, you should have some of this assignment already written

```{r}
#| label: setup
#| echo: false
#| message: false

library(tidyverse)
```

## Question One (copy over from class)

**a)** Add a level-one heading "Data"
**b)** Write a sentance or two about the data you're using for you final project
**c)** Make the source of your data (e.g., IPEDS) _italic_
**d)** Change the header title to something appropriate for your final report
**e)** Change the header author to your name
**f)** Change the header date so that it uses the current date whenever it is rendered
**g)** Set the output format to create a pdf (either `pdf` or `typst`)


## Question Two (to be done after class)

**a)** Read in at least one data file you intend to use for your final project

```{r}
#| label: 2a


```

**b)** Include a plot showing the distribution of your primary outcome/variable of interest

> Bonus: Caption and number it using Quarto's automatic system

```{r}
#| label: 2b


```

**c)**  Choose a categorical variable in your dataset, get the counts and percentages in each category (a Data Viz I throwback), and turn that into a nicely formatted `kable()`

> Bonus: Caption and number it using Quarto's automatic system

```{r}
#| label: 2c


```

**d)** Find an article that you think might be relavent to your final project, save it using Zotero, and then cite it using Quarto's Zotero integration

> Bonus: Use APA 7 citation style and place the bibliography on a new page

**e)** Save the file as `reproducible-report.qmd`

Congratulations, you've officially started the Quarto document for your final project!

```{=html}
<!--
Once complete, turn in the .qmd file (must render successfully) to Canvas by Tuesday 12:00pm following the lesson.
Assignments will be graded before next lesson on Wednesday in line with the grading policy outlined in the syllabus.
-->
```